### 2019-03-04 README.Rmd
submission hurdle

@@

- **data-raw:** Raw data processing.
- **data:** Processed data.
- **R:** Supporting R functions
- **vignettes:** Analysis paper and results.

@@

- Install R (analysis run with `3.5.2`) and Rstudio.

>>>>

[Sam Abbott](https://www.samabbott.co.uk), Hannah Christensen, Nicky Welton, Ellen Brooks-Pollock

@@

- **data-raw:** Raw data processing.
- **data:** Processed data.
- **R:** Supporting R functions
- **vignettes:** Analysis paper and results.
- **peer-review** Documentation required for peer review.

@@

- Install R (analysis run with `3.5.2`) and Rstudio (altnernatively use Docker as outlined below).
